Generalized Universe Hierarchies and First-Class Universe Levels

### 2021-04-19 arxivsub/preprint.tex
typo
update arxiv sub with fixes

%\nolinenumbers %uncomment to disable line numbering

%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

@@

Predicative hierarchies originate from Russell's ramified type theories
\cite{principia}. In the more modern formulations of type theory, Martin-Löf
proposed a countable predicative hierarchy \cite{martinlof73predicative}, as a
way to remedy the inconsistency of the previous version of the theory (which
assumed type-in-type). Harper and Pollack described universe inference with
level assignments and also a form of level polymorphism \cite{harperpollack}.
Sterling \cite{sterling2019algebraic} gave an algebraic specification much like
ours for a type theory with countable cumulative universes, and prove canonicity
for it.

>>>>

\nolinenumbers %uncomment to disable line numbering
\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

@@

Predicative hierarchies originate from Russell's ramified type theories
\cite{principia}. In the more modern formulations of type theory, Martin-Löf
proposed a countable predicative hierarchy \cite{martinlof73predicative}, as a
way to remedy the inconsistency of the previous version of the theory (which
assumed type-in-type). Harper and Pollack described universe inference with
level assignments and also a form of level polymorphism \cite{harperpollack}.
Sterling \cite{sterling2019algebraic} gave an algebraic specification much like
ours for a type theory with countable cumulative universes, and proved canonicity
for it.
